A multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-05-24 manuscript/manuscript.tex
references

\bibitem{ } Cox, D. R. (1972). Regression models and life tables (with
discussion).  \textit{Journal of the Royal Statistical Society, Series B}
\textbf{34,} 187--200.

\bibitem{ }  Hastie, T., Tibshirani, R., and Friedman, J. (2001). \textit{The 
Elements of Statistical Learning: Data Mining, Inference, and Prediction}.
New York: Springer.

>>>>

\bibitem{ } Lagona F, Picone M. Model-based clustering of multivariate skew data with circular components and missing values. \textit{Journal of Applied Statistics}. 2012 May 1;39(5):927-45.

\bibitem{ } Lee SX, McLachlan GJ. Model-based clustering and classification with non-normal mixture distributions. Statistical Methods \& Applications. 2013 Nov 1;22(4):427-54.

\bibitem{ } Fr\"{u}hwirth-Schnatter S, Pyne S. Bayesian inference for finite mixtures of univariate and multivariate skew-normal and skew-t distributions. Biostatistics. 2010 Jan 27;11(2):317-36.

\bibitem{ } Tiao GC, Zellner A. On the Bayesian estimation of multivariate regression. \textit{Journal of the Royal Statistical Society}: Series B (Methodological). 1964 Jul;26(2):277-85.

\bibitem{ } Zhou X, Reiter JP. A note on Bayesian inference after multiple imputation. \textit{The American Statistician}. 2010 May 1;64(2):159-63.

\bibitem{ } Vrbik I, Mcnicholas PD. Parsimonious skew mixture models for model-based clustering and classification. \textit{Computational Statistics \& Data Analysis}. 2014 Mar 1;71:196-210.

\bibitem{ } Melnykov V, Maitra R. Finite mixture models and model-based clustering. \textit{Statistics Surveys}. 2010;4:80-116.

\bibitem{ } Lee SX, Mclachlan GJ. On mixtures of skew normal and skew $$ t $$-distributions. \textit{Advances in Data Analysis and Classification}. 2013 Sep 1;7(3):241-66.

\bibitem{ } Lin TI, Wang WL, McLachlan GJ, Lee SX. Robust mixtures of factor analysis models using the restricted multivariate skew-t distribution. \textit{Statistical Modelling}. 2018 Feb;18(1):50-72.
